On The Difficulty of Computing Non-Commutative Signature Gröbner Bases

### 2022-02-02 article_issac.tex
Un peu plus sur les langages réguliers.

\begin{proposition}
  Leading monomials of syzygies of $F=\{g_1,\dots,g_{11}\}$ do not form a regular language
\end{proposition}
\begin{proof}
  For every $n \geq 1$, $g_{11}a^nb^ne$ is the leading monomial of the syzygy:

@@

Notice that $F=\{g_1,\dots,g_{11}\}$ has no reason to have a finite Gröbner basis. However, we construct a new set $F'$ by adding to $F$ the polynomial $\infty$ and all polynomials of the form $\infty-\alpha$, for letters $\alpha$ different from $\infty$. Then $F'$ admits the reduced Gröbner basis which contains each letter.
Now, let $\mathscr{B}$ be the sets of leading monomials of syzygies of $F'$.
As our ideal is homogeneous,
the set of the
leading monomials of the syzygies
is the same as the set of the leading
monomials of the homogeneous syzygies.
Thanks to the way we defined our order,
if $\sigma \in Syz(F')$ is homogeneous,
and
if $\infty$ appears in a $l \LM(g_i) r$,
for some $l \varepsilon_i r$ 
a term of $\sigma.$ 
then 
$\infty$ appears in $l' \LM(g_j) r'$
where $l' \varepsilon_j r'$ is the $\LM$
of $\sigma.$
Thus $\mathscr{A} \cap \mathscr{C}=\mathscr{B} \cap \mathscr{C}$. Since $\mathscr{C}$ is a regular language and $\mathscr{A} \cap \mathscr{C}$ is not a regular language, $\mathscr{B}$ is not a regular language. Hence, we have constructed a set $F'$ of polynomials that admit a finite Gröbner basis whose set of leading monomials of syzygies does not form a regular language.

>>>>

\begin{proposition}
  Leading monomials of syzygies of $F=\{g_1,\dots,g_{11}\}$ do not form a regular language.
  \label{prop:exp_pas_regulier}
\end{proposition}
\begin{proof}
  For every $n \geq 1$, $g_{11}a^nb^ne$ is the leading monomial of the syzygy:

@@

\begin{cor}
There is a set $F'$ of polynomials which
admits a finite Gröbner basis
and whose set of leading monomials of syzygies does not form a regular language. 
\end{cor}
\begin{proof}
We carry on with the notations of Prop. \ref{prop:exp_pas_regulier} and
its proof.
Notice that $F=\{g_1,\dots,g_{11}\}$ has no reason to have a finite Gröbner basis. However, we construct a new set $F'$ by adding to $F$ the polynomial $\infty$ and all polynomials of the form $\infty-\alpha$, for letters $\alpha$ different from $\infty$. Then $F'$ admits the reduced Gröbner basis which contains each letter.
Now, let $\mathscr{B}$ be the sets of leading monomials of syzygies of $F'$.
As our ideal is homogeneous,
the set of the
leading monomials of the syzygies
is the same as the set of the leading
monomials of the homogeneous syzygies.
Thanks to the way we defined our order,
if $\sigma \in Syz(F')$ is homogeneous,
and
if $\infty$ appears in a $l \LM(g_i) r$,
for some $l \varepsilon_i r$ 
a term of $\sigma.$ 
then 
$\infty$ appears in $l' \LM(g_j) r'$
where $l' \varepsilon_j r'$ is the $\LM$
of $\sigma.$
Thus $\mathscr{A} \cap \mathscr{C}=\mathscr{B} \cap \mathscr{C}$. Since $\mathscr{C}$ is a regular language and $\mathscr{A} \cap \mathscr{C}$ is not a regular language, $\mathscr{B}$ is not a regular language. Hence, we have constructed a set $F'$ of polynomials that admit a finite Gröbner basis whose set of leading monomials of syzygies does not form a regular language. 
\end{proof}
